%-------------------------
% Resume in Latex
% Author : Jake Gutierrez
% Based off of: https://github.com/sb2nov/resume
% License : MIT
%------------------------

\documentclass[letterpaper,11pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}
\usepackage[utf8]{inputenc}
\usepackage{fontawesome5}
\usepackage{multicol}
\setlength{\multicolsep}{-3.0pt}
\setlength{\columnsep}{-1pt}
\input{glyphtounicode}

\pagestyle{fancy}
\fancyhf{}
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

\addtolength{\oddsidemargin}{-0.6in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1.19in}
\addtolength{\topmargin}{-.7in}
\addtolength{\textheight}{1.4in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

\titleformat{\section}{
  \vspace{-4pt}\scshape\raggedright\large\bfseries
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

\pdfgentounicode=1

%-------------------------
% Custom commands
\newcommand{\resumeItem}[1]{
  \item\small{
    {#1 \vspace{-2pt}}
  }
}

\newcommand{\classesList}[4]{
    \item\small{
        {#1 #2 #3 #4 \vspace{-2pt}}
  }
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-2pt}\item
    \begin{tabular*}{1.0\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} & \textbf{\small #2} \\
      \textit{\small#3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubSubheading}[2]{
    \item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \textit{\small#1} & \textit{\small #2} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeProjectHeading}[2]{
    \item
    \begin{tabular*}{1.001\textwidth}{l@{\extracolsep{\fill}}r}
      \small#1 & \textbf{\small #2}\\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubItem}[1]{\resumeItem{#1}\vspace{-4pt}}

\renewcommand\labelitemi{$\vcenter{\hbox{\tiny$\bullet$}}$}
\renewcommand\labelitemii{$\vcenter{\hbox{\tiny$\bullet$}}$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=0.0in, label={}]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

%-------------------------------------------
%%%%%%  RESUME STARTS HERE  %%%%%%%%%%%%%%%%%%%%%%%%%%%%

\begin{document}

%----------HEADING----------
\begin{center}
    {\Huge \scshape Abdelrahman Nassar} \\ \vspace{5pt}
    Full Stack Software Engineer \textbar{} Cloud \& DevOps \textbar{} SaaS Builder \\ \vspace{5pt}
    Cairo, Egypt \\ \vspace{5pt}
    \small
    \href{mailto:abdelrhman.ahmed.nassar@gmail.com}{\raisebox{-0.2\height}\faEnvelope\  \underline{abdelrhman.ahmed.nassar@gmail.com}} ~
    \href{https://www.linkedin.com/in/abdelrahmannassar}{\raisebox{-0.2\height}\faLinkedin\ \underline{linkedin.com/in/abdelrahmannassar}}  ~
    \href{https://abdelrahman-nassar.com}{\raisebox{-0.2\height}\faGlobe\ \underline{abdelrahman-nassar.com}}
    \vspace{-8pt}
\end{center}

%-----------SUMMARY-----------
\section{Summary}
\vspace{-3pt}
\resumeSubHeadingListStart
  \resumeItem{Full Stack Engineer and Computer Engineering student with hands-on experience building and deploying production SaaS platforms, ERP systems, and scalable web applications using MERN stack, Next.js, and cloud infrastructure.}
  \resumeItem{AWS Certified (Cloud Practitioner \& Solutions Architect Associate) with practical experience in Docker, CI/CD pipelines, VPS deployment, and Nginx — passionate about cloud-native architecture and currently exploring GenAI integration and LLM-powered product features.}
  \resumeItem{Delivered cross-functional solutions serving 20,000+ users across education and business sectors, collaborating with clients, stakeholders, and multi-role teams including HR, accountants, teachers, and administrators.}
  \resumeItem{Seeking an engineering internship to contribute to impactful, innovative tech and accelerate professional growth within a structured mentorship environment.}
\resumeSubHeadingListEnd
\vspace{-10pt}


%-----------EDUCATION-----------
\section{Education}
  \resumeSubHeadingListStart
    \resumeSubheading
      {Al-Azhar University}{July 2023 -- July 2028}
      {Bachelor of Electrical Systems and Computer Engineering (ESCE)}{Cairo, Egypt}
      \resumeItemListStart
        \resumeItem{Computer Engineering Department — Currently in 2nd year}
        \resumeItem{Academic Excellence: 2nd Place in Engineering Preparatory Year (April 2024)}
        \resumeItem{Top High School Graduate Award — 99\% Score in Al-Azhar Secondary School Certificate}
      \resumeItemListEnd
  \resumeSubHeadingListEnd

%-----------CERTIFICATIONS (elevated)----------
\section{Certifications}
\resumeSubHeadingListStart
    \resumeSubheading{AWS Certifications}{2022 -- 2023}{Cloud Practitioner \& Solutions Architect Associate}{}
    \resumeSubheading{Professional Development}{2022 -- 2024}{Full Stack Engineering Coursework}{}
        \resumeItemListStart
            \resumeItem{NodeJS — The Complete Guide (MVC, REST APIs, GraphQL, Deno) — 40 hours}
            \resumeItem{React — The Complete Guide (incl. Next.js, Redux) — 71 hours}
            \resumeItem{The Complete JavaScript Course 2022: From Zero to Expert — 69 hours}
        \resumeItemListEnd
\resumeSubHeadingListEnd

%-----------EXPERIENCE-----------
\section{Experience}
  \resumeSubHeadingListStart

    \resumeSubheading
      {Learn Shift}{Sep 2025 -- Present}
      {Lead Developer \& Software Architect}{Cairo, Egypt}
      \resumeItemListStart
        \resumeItem{Architected and delivered custom LMS platforms for multiple education businesses, collaborating closely with clients, teachers, and operations teams to translate business requirements into scalable technical solutions.}
        \resumeItem{Designed a monorepo architecture with shared packages, Docker-based deployment, and GitHub Actions CI/CD — reducing new client onboarding time to under one day on Digital Ocean VPS.}
        \resumeItem{Led cross-functional execution across frontend, backend, infrastructure, and client delivery using Agile workflows, ensuring on-time delivery across concurrent projects.}
        \resumeItem{Mentored and coordinated junior developers, conducting code reviews and enforcing clean code standards.}
      \resumeItemListEnd

    \resumeSubheading
      {Shift Up Solutions}{June 2025 -- September 2025}
      {Full-Stack Developer Intern}{Cairo, Egypt}
      \resumeItemListStart
        \resumeItem{Contributed to real-world MERN stack projects with focus on scalable web application architecture in a professional team environment.}
        \resumeItem{Built optimized React components and RESTful APIs using Express.js and MongoDB, following clean code practices and Git version control workflows.}
        \resumeItem{Collaborated across feature development, debugging, and UI/UX improvements within an Agile sprint cycle.}
      \resumeItemListEnd

    \resumeSubheading
      {Kalbonyan Elmarsos}{March 2022 -- November 2022}
      {Software Engineering Intern}{Egypt}
      \resumeItemListStart
        \resumeItem{Completed an intensive full-stack development training program covering modern web technologies — built 8+ real-world projects including Omnifood, Bankist, Mapty, and Forkify.}
        \resumeItem{Won 1st Place in Kalbonyan Elmarsos Programming Competition (March 2023).}
      \resumeItemListEnd

  \resumeSubHeadingListEnd

%-----------PROJECTS-----------
\section{Featured Projects}
\vspace{-5pt}
\resumeSubHeadingListStart

%================ LMS PLATFORM ================%
\resumeProjectHeading
  {\href{https://heba-elsayed.com}{\underline{\textbf{LMS Platform — Learn Shift Core Product}}} $|$ \emph{Next.js, NestJS, MongoDB, Redis, Docker, GitHub Actions}}{Jan 2025 -- Present}
  \resumeItemListStart
    \resumeItem{Production LMS ecosystem serving 20,000+ students across multiple live deployments — the core product of the Learn Shift platform (\href{https://learn-shift.org}{learn-shift.org}).}
    \resumeItem{Built three interconnected apps: a Next.js student portal (Fawry payments, video protection, WhatsApp alerts), a React.js admin dashboard (drag-and-drop course builder, real-time analytics), and a 40+ module NestJS REST API (JWT/RBAC, Redis caching, BullMQ queues, Grafana monitoring).}
    \resumeItem{Containerized with Docker and deployed via CI/CD on Digital Ocean VPS with Nginx reverse proxy — engineering decisions rooted in cloud-native scalability and operational reliability.}
  \resumeItemListEnd
  \vspace{-13pt}

%================ MODAWIM ================%
\resumeProjectHeading
  {\href{https://modawim.com}{\underline{\textbf{Modawim — Productivity SaaS Platform}}} $|$ \emph{Next.js, TypeScript, PostgreSQL, Drizzle ORM, Redis}}{2025 -- 2026}
  \resumeItemListStart
    \resumeItem{Designed, built, and launched a full-stack SaaS productivity platform serving thousands of users — offering integrated tools (Tasks, Goals, Habits, Journaling, Notes, Calendar) backed by productivity psychology research.}
    \resumeItem{Engineered a reusable SaaS starter template covering OAuth, 4-role RBAC, Firebase push notifications, payment gateway with coupon support, support ticketing, blog, newsletter, Playwright E2E tests, PWA, and CI/CD — now forkable as a foundation for future products.}
    \resumeItem{Handled the full product lifecycle end-to-end: architecture, backend APIs, frontend UI, infrastructure, and user-facing delivery — demonstrating ownership across all engineering layers.}
  \resumeItemListEnd
  \vspace{-13pt}

%================ AL-MOSTAFA ERP ================%
\resumeProjectHeading
  {\href{https://almostafa.academy}{\underline{\textbf{Al-Mostafa Kindergarten ERP System}}} $|$ \emph{Next.js, NestJS, MongoDB, Redis, Docker}}{2026}
  \resumeItemListStart
    \resumeItem{Built an enterprise ERP system for a nursery of 100+ employees and 1,000+ children — covering 14 modules: HR and payroll, student academic evaluations, parent portal, transportation routing, admissions, billing with installment plans, accounting reports, and multi-channel notifications.}
    \resumeItem{Designed for 8 distinct user roles (admin, HR, teachers, accountants, receptionists, transport supervisors, parents) — collaborated directly with department heads to gather requirements and iterate on workflows, with automated PDF generation across all departments.}
  \resumeItemListEnd
  \vspace{-13pt}

%================ AL-AZHAR SHOWCASE ================%
\resumeProjectHeading
  {\href{https://al-azhar-electronics.netlify.app}{\underline{\textbf{Al-Azhar Engineering Showcase Platform}}} $|$ \emph{Next.js, TypeScript, Tailwind CSS, Supabase}}{Apr -- May 2025}
  \resumeItemListStart
    \resumeItem{Built the official project archive platform for Al-Azhar's Computer \& Systems Engineering department — hosting 59+ projects and 75+ teams, with search, auto-generated student portfolios, and team profile pages.}
    \resumeItem{Formally adopted by university leadership (President, Dean, Department Head) as the permanent submission system — presented at the AZ-SENCS exhibition and led directly to a professional internship offer from a recruiter on-site.}
  \resumeItemListEnd

\resumeSubHeadingListEnd


%-----------SKILLS-----------
\section{Technical Skills}
\resumeSubHeadingListStart
\resumeItem{\textbf{Frontend:} React.js, Next.js, TypeScript, Tailwind CSS, Redux, Zustand}
\resumeItem{\textbf{Backend:} Node.js, Express.js, NestJS, REST APIs, JWT, RBAC}
\resumeItem{\textbf{Databases:} MongoDB, PostgreSQL, Redis, Supabase, Drizzle ORM}
\resumeItem{\textbf{Cloud \& DevOps:} AWS (Certified), Docker, GitHub Actions CI/CD, VPS, Nginx, Linux}
\resumeItem{\textbf{Exploring:} GenAI integration, LLM APIs, prompt engineering}
\resumeItem{\textbf{Tools:} Git, Postman, Swagger, Cloudinary, Figma, Sentry, Grafana}
\resumeSubHeadingListEnd

%-----------AWARDS-----------
\section{Awards \& Recognition}
\resumeSubHeadingListStart
    \resumeSubheading{AZ-SENCS Engineering Exhibition}{May 2025}{Participant — Presidential Recognition}{Al-Azhar University}
        \resumeItemListStart
            \resumeItem{Presented project to University President Prof. Dr. Salama Dawood and Faculty Dean}
            \resumeItem{Project officially adopted by university and hosted on institutional servers}
        \resumeItemListEnd

    \resumeSubheading{Kalbonyan Elmarsos Programming Competition}{March 2023}{1st Place}{}
\resumeSubHeadingListEnd

%-----------ACHIEVEMENTS-----------
\section{Achievements}
\vspace{-3pt}
\resumeItemListStart
  \resumeItem{Built systems used by 20,000+ users across production deployments}
  \resumeItem{70+ GitHub repositories — 100+ stars}
  \resumeItem{7,000+ LinkedIn followers}
  \resumeItem{200+ Codeforces problems solved}
\resumeItemListEnd

%-----------LANGUAGES-----------
\section{Languages}
\vspace{-3pt}
\resumeItemListStart
  \resumeItem{Arabic: Native}
  \resumeItem{English: Professional Working Proficiency (B2/C1)}
\resumeItemListEnd

\end{document}